---
title: "case_study"
output: html_document
date: "`r Sys.Date()`"
---

```{r}
library(tidyverse)
library(ggridges)
library(leaflet)
library(p8105.datasets)

data(nyc_airbnb)

nyc_airbnb = 
  nyc_airbnb |>
  rename(borough = neighbourhood_group) |>
  mutate(stars = review_scores_location / 2)
```

## Brainstorm questions

- Where are AirBNBs expensive?
  - Borough? Neighborhood?
  - Do other factors (room type) affect price? What about rating
- How long are AirBNBs active?
  - Are AirBNBs illegal and do they get shut down?
- Which units have the most availbability?
- How is review score impacted by location?
- How many apts are run by one host?


## Do some EDA

```{r}
nyc_airbnb |>
  count(borough)
```

```{r}
nyc_airbnb |>
  group_by(borough, room_type) |>
  summarize(mean_price = mean(price)) |>
  pivot_wider(
    names_from = room_type,
    values_from = mean_price
  )
```

```{r}
nyc_airbnb |>
  ggplot(aes(x = price)) +
  geom_histogram() +
  facet_grid(borough ~ room_type)
```

```{r}
nyc_airbnb |>
  filter(price > 1000, room_type == "Entire home/apt") |>
  ggplot(aes(x = price)) +
  geom_histogram() +
  facet_grid(. ~ borough)
```

```{r}
nyc_airbnb |>
  filter(
    price < 1000,
    room_type == "Entire home/apt",
    borough == "Manhattan") |>
  group_by(neighbourhood) |>
  summarize(
    n_opt = n(),
    mean_price = mean(price)
  ) |>
  arrange(desc(mean_price))
```

```{r eval=FALSE}
nyc_airbnb |>
  filter(
    price < 1000,
    room_type == "Entire home/apt",
    borough == "Manhattan") |>
  mutate(neighbourhood = fct_reorder(neighbourhood, price)) |>
  ggplot(aes(x = neighbourhood, y = price)) +
  geom_density_ridges()
```

## Try to make a map

```{r}
nyc_airbnb |>
  filter(
    price < 1000,
    room_type == "Entire home/apt",
    borough == "Manhattan") |>
  ggplot(aes(x = lat, y = long, color = price)) +
  geom_point()
```

Try something else 

```{r}
nyc_airbnb |>
  filter(
    price < 1000,
    room_type == "Entire home/apt",
    borough == "Manhattan") |>
  sample_n(500) |>
  leaflet() |>
  addTiles() |>
  addMarkers(~lat, ~long)
```

```{r}
nyc_airbnb |>
  filter(
    price < 1000,
    room_type == "Entire home/apt",
    borough == "Manhattan") |>
  sample_n(500) |>
  leaflet() |>
  addProviderTiles(providers$CartoDB.Positron) |>
  addCircleMarkers(~lat, ~long, radius = .5)
```









